Andres Karjus

### 2021-11-12 index.Rmd
news fix

- [Conference on Complex Systems 2021](https://ccs2021.univ-lyon1.fr/) (October 2021) | [slides](https://andreskarjus.github.io/talks/ccs2021/Karjus_CCS2021_Capturing_aesthetic_complexity.pdf)
- [Protolang 7](https://blogs.phil.hhu.de/protolang7/programme/) (September 2021) | [slides](https://andreskarjus.github.io/slides/andres_karjus_protolang7.pdf)
- [TÜling](https://www.keel.ut.ee/et/tuling) (April 2021)
- [Colloquium for Computational Linguistics and Linguistics in Stuttgart](https://www.ims.uni-stuttgart.de/en/research/colloquium/) | [Slides](https://andreskarjus.github.io/talks/stuttgart2021/andres_karjus_lexical_dynamics_slides_stuttgart2021.pdf) | [Recording](https://www.ims.uni-stuttgart.de/documents/aktuelles/veranstaltungen/210111-Karjus-Talk-Colloq-Recording.mp4)
- [RUSE 2019](http://rusesymposium.org.uk/). Slides [here](https://andreskarjus.github.io/ruse2019).
- [CL2019](http://www.cl2019.org/). Slides [here](https://andreskarjus.github.io/cl2019talk.html).
- [Culture Conference 2019](https://culture-conference.com/programme-2019/), Poster [here](https://andreskarjus.github.io/lexcom_poster).
- [Inaugural ISLE workshop](https://www.comparativelinguistics.uzh.ch/en/events/ISLE-inaugural-workshop.html) | _Modelling lexical interactions in diachronic corpora_ |  [poster](https://andreskarjus.github.io/isle_poster)
- University of Edinburgh [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) seminar series | _Challenges in detecting evolutionary forces in language change using diachronic corpora_ | [slides](https://andreskarjus.github.io/evoforces_cletalk/slides.html) | [code](https://github.com/andreskarjus/wfsim_fit)
- Corpus Linguistics in Scotland Network Meeting, _Topical Fluctuations and Lexical Interactions in Diachronic Corpora_

>>>>

- [Conference on Complex Systems 2021](https://ccs2021.univ-lyon1.fr/) (October 2021) | [slides](https://andreskarjus.github.io/talks/ccs2021/Karjus_CCS2021_Capturing_aesthetic_complexity.pdf)
- [Protolang 7](https://blogs.phil.hhu.de/protolang7/programme/) (September 2021) | [slides](https://andreskarjus.github.io/talks/andres_karjus_protolang7.pdf)
- [TÜling](https://www.keel.ut.ee/et/tuling) (April 2021)
- [Colloquium for Computational Linguistics and Linguistics in Stuttgart](https://www.ims.uni-stuttgart.de/en/research/colloquium/) | [Slides](https://andreskarjus.github.io/talks/stuttgart2021/andres_karjus_lexical_dynamics_slides_stuttgart2021.pdf) | [Recording](https://www.ims.uni-stuttgart.de/documents/aktuelles/veranstaltungen/210111-Karjus-Talk-Colloq-Recording.mp4)
- [RUSE 2019](http://rusesymposium.org.uk/). Slides [here](https://andreskarjus.github.io/ruse2019).
- [CL2019](http://www.cl2019.org/). Slides [here](https://andreskarjus.github.io/cl2019talk.html).
- [Culture Conference 2019](https://culture-conference.com/programme-2019/), Poster [here](https://andreskarjus.github.io/lexcom_poster).
- [Inaugural ISLE workshop](https://www.comparativelinguistics.uzh.ch/en/events/ISLE-inaugural-workshop.html) | _Modelling lexical interactions in diachronic corpora_ |  [poster](https://andreskarjus.github.io/isle_poster)
- University of Edinburgh [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) seminar series | _Challenges in detecting evolutionary forces in language change using diachronic corpora_ | [slides](https://andreskarjus.github.io/evoforces_cletalk/slides.html) | [code](https://github.com/andreskarjus/wfsim_fit)
- Corpus Linguistics in Scotland Network Meeting, _Topical Fluctuations and Lexical Interactions in Diachronic Corpora_

### 2021-11-12 news.Rmd
news
news fix

- Now out in [Cognitive Science](https://doi.org/10.1111/cogs.13035) and also presented at Protolang 7 - "Conceptual similarity and communicative need shape colexification: an experimental study" (08.09.2021) | [pdf](https://andreskarjus.github.io/papers/Karjus_2021__Conceptual_Similarity_and_Communicative_Need_Shape_Colexification_An_Experimental_Study__Cognitive_Science.pdf) | [Protolang slides](https://andreskarjus.github.io/slides/andres_karjus_protolang7.pdf) | [tweet-summary](https://twitter.com/AndresKarjus/status/1435536919459418113)

>>>>

- Talk at the [Conference on Complex Systems 2021](https://ccs2021.univ-lyon1.fr/) in Lyon: "Capturing aesthetic complexity in art using compression ensembles" (29.10.2021) | [slides here](https://andreskarjus.github.io/talks/ccs2021/Karjus_CCS2021_Capturing_aesthetic_complexity.pdf)

- Now out in [Cognitive Science](https://doi.org/10.1111/cogs.13035) and also presented at Protolang 7 - "Conceptual similarity and communicative need shape colexification: an experimental study" (08.09.2021) | [pdf](https://andreskarjus.github.io/papers/Karjus_2021__Conceptual_Similarity_and_Communicative_Need_Shape_Colexification_An_Experimental_Study__Cognitive_Science.pdf) | [Protolang slides](https://andreskarjus.github.io/talks/andres_karjus_protolang7.pdf) | [tweet-summary](https://twitter.com/AndresKarjus/status/1435536919459418113)
